Title

### 2022-04-27 thesis/conclusion.tex
change subsection to section and labels

\section{Conclusion} \label{sec:conclusion}
This paper proposes an energy model based on the operating frequency and the number of cores for a shared memory system. This model serves as a reference for DVFS and DPM optimization problems.

@@

\subsection{Conclusions and Future Works Pascal}\label{sec:conclusions_pascal}

@@

\subsection{Conclusion fingerprint}

@@

>>>>

\section{Conclusion Models} \label{sec:conclusion_models}
This paper proposes an energy model based on the operating frequency and the number of cores for a shared memory system. This model serves as a reference for DVFS and DPM optimization problems.

@@

\subsection{Conclusions and Future Works Pascal} \label{sec:conclusions_pascal}

@@

\subsection{Conclusion fingerprint tool}

@@

\section{Conclusion and future work: Phases}
The main conclusion of this work was that in HPC enviroment we don't need a lot of phases to optimize the energy consumption given that for one phase we can compute the optimal energy.

The final idea is to use the information of the best phase to find a performance metric that can provide us this division, in future work we intend to compute this metrics using combination of hardware performance counters enabling optimal phase division in real time. This can improve current DVFS algorithms giving them an workload metric that can improve the energy savings.

### 2022-04-27 thesis/experiments/experiments.tex
change subsection to section and labels

\section{Validation the framework}\label{sec:validation_the_framework}
In this Section, we discuss the measurements and simulation results for three distinct cases, including two real applications. We also demonstrate how external libraries and standalone visualization tools can be used to render the collected data and investigate performance aspects such as the program's scalability capacity.

\subsection{Configuration} \label{subsec:configuration_pascal}

@@

\subsection{Pascal Analyzer Validation}\label{sec:results_pascal}

@@

% \begin{figure}[H]
% \centering
% \includegraphics[width=\linewidth]{pascalanalyzer/figures/results/efficiency_openmc_detailed.png}
% \caption{Efficiency for OpenMC}
% \label{fig:efficiency_openmc_detailed}
% \end{figure}
\subsection{Fingerprint Tool validation}

@@

\subsubsection{ACCURACY COMPARISON}

@@

\subsubsection{CLUSTERING}

>>>>

\section{Pascal framework validation} \label{sec:pascal_framework_validation}
In this Section, we discuss the measurements and simulation results for three distinct cases, including two real applications. We also demonstrate how external libraries and standalone visualization tools can be used to render the collected data and investigate performance aspects such as the program's scalability capacity.

@@

\subsection{Case of study}\label{subsec:pfv_case_of_study}

@@

% \begin{figure}[H]
% \centering
% \includegraphics[width=\linewidth]{pascalanalyzer/figures/results/efficiency_openmc_detailed.png}
% \caption{Efficiency for OpenMC}
% \label{fig:efficiency_openmc_detailed}
% \end{figure}
\section{Fingerprint Tool validation} \label{sec:fingerprint_tool_validation}

@@

%\subsection{Accuracy comparison} \label{subsec:ftv_accuracy_comparison}

@@

\subsubsection{Case of study} \label{subsec:ftv_case_of_study}

### 2022-04-27 thesis/fingerprint/fingerprint.tex
change subsection to section and labels

\section{Fingerprint tool}
The analysis of application performance is essential to better exploit its potential on High-Performance Computing (HPC) architectures. Access to performance counters, available in modern processors, allows collecting key information about program behavior to provide the most appropriate HPC execution strategy.
In this context, we have developed an accurate tool based on performance counters, which facilitates modeling, fingerprinting, behavior comparison and clustering of applications.
It provides a high-level Python API for accessing and configuring performance counters; while execution and counters data gathering is  performed by a C++ module to reduce overhead. 
Indeed, the accuracy of this multiplatform tool was also compared to existing alternatives.  
Key features, such as performance counters collection, post-processing, and comparison, enable fingerprinting of applications, an important step in understanding program behavior for later classification and optimization according to the parameters characterizing the target HPC platform.
For demonstration purposes, the tool was used in the clustering of Polybench applications, a frequently used benchmark set for kernels monitoring. 
%%, a frequently used benchmark for compiler optimization and testing. 
This clustering facilitated the identification of applications with similar and comparable behaviors in terms of input size, data access and transfer, resource utilization and computation, which facilitates the creation of test sets for a given environment based on specific measurement parameters.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Introduction}

@@

\subsection{Related Work}

@@

\subsection{Reading Performance Counters}

@@

\subsection{Implementation}

@@

\subsubsection{ARCHITECTURE}

@@

\subsubsection{POST-PROCESSING}
\label{sec:posprocessing}
% With this API we create clusterize the applications of Polybench applications.

>>>>

\section{Profiling with performance counters} \label{sec:profiling_with_performance_counters}
The analysis of application performance is essential to better exploit its potential on High-Performance Computing (HPC) architectures. Access to performance counters, available in modern processors, allows collecting key information about program behavior to provide the most appropriate HPC execution strategy.
In this context, we have developed an accurate tool based on performance counters, which facilitates modeling, fingerprinting, behavior comparison and clustering of applications.
It provides a high-level Python API for accessing and configuring performance counters; while execution and counters data gathering is  performed by a C++ module to reduce overhead. 
Indeed, the accuracy of this multiplatform tool was also compared to existing alternatives.  
Key features, such as performance counters collection, post-processing, and comparison, enable fingerprinting of applications, an important step in understanding program behavior for later classification and optimization according to the parameters characterizing the target HPC platform.
For demonstration purposes, the tool was used in the clustering of Polybench applications, a frequently used benchmark set for kernels monitoring. 
%%, a frequently used benchmark for compiler optimization and testing. 
This clustering facilitated the identification of applications with similar and comparable behaviors in terms of input size, data access and transfer, resource utilization and computation, which facilitates the creation of test sets for a given environment based on specific measurement parameters.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Collecting performance counters} \label{sec:collecting_performance_countersl}

@@

\section{State of the art performance counters APIs} \label{sec:state_of_the_art_performance_counters_APIs}

@@

\section{Accounting for errors and limitations} \label{sec:accounting_for_errors_and_limitations}

@@

\section{Implementing a tool to read performance counters precisely} \label{sec:implementing_a_tool_to_read_performance_counters_precisely}

@@

\section{PMC tool architecture} \label{sec:PMC_tool_architecture}

@@

\section{Post-processing} \label{sec:posprocessing}
% With this API we create clusterize the applications of Polybench applications.

### 2022-04-27 thesis/optmization.tex
change subsection to section and labels

\subsection{Verifying Hypothesis}

@@

\subsection{Frequency and Voltage Relation}
One of the assumptions was that the frequency and the voltage have a linear relationship, as indicated by ~\cref{eq:f_v}. To verify that, we build an experiment that sets the frequency to a specific value while sampling the voltage using the APERF and MPERF registers that provide feedback on the current CPU frequency. The average result of the sampling voltages is shown in  \cref{fig:freq_volt_rel}, where we can observe a near-perfect linear relation. This is because manufacturers implement this curve in the processors, using tables that relate ranges of frequencies to voltages so that they can precisely define any curve that will better suit their design.

@@

\subsection{Input Size and Instructions}
We ran the applications with different inputs assuming  linear growth in the amount of work for one input to the other when building our model. However, measuring and controlling the amount of work would require much instrumentation and tuning to find an input corresponding to a certain amount of work. Therefore, to build our models, we use the time to reference the amount of work, assuming that the work is proportional to the executing time. \cref{fig:time_input} corresponds to the verification of this supposition.

@@

\section{Fitting the Models} \label{subsec:fitting}
To find the parameters of  \cref{eq:en_final}, 10 uniformly random configurations of frequencies ($f$), cores ($p$) and inputs ($N$) were chosen from the range $1<=p<=32$, $1.2<=f<=2.2$ and $1<=N<=5$, respectively. The application was executed for each chosen configuration, and the measured energy and time values were collected. For the input size, if we assume that all CPU instructions take approximately the same time to execute, the number of basic operations will be directly correlated with the time. Thus, we can estimate the input size by looking at the execution time, allowing us to divide a large input size into several smaller ones, knowing their relationship, as performed in the work of Oliveira ~\cite{Oliveira2018ApplicationCharacterization}. The unity can also vary depending on the definition. For simplicity, we assign numbers from 1 to 10, increasing the problem linearly, so it is also possible to interpolate any input in between these values.

@@

\section{Measured versus Modeled Energy}
\label{subsec:measuredversusmodeledenergy}

@@

\subsection{Frequency $\times$ Cores}
\cref{fig:en_eq_freq_cores_fc} plots the measured and modeled energy consumption for some of the applications modeled. In addition,  some of the possible shapes that the model can take while varying the number of active cores, and operating frequency, are shown.%please confirm that the intended meaning has been retained.
% yes its the same

@@

	\caption{Example fit for a specific input size: Blackscholes (\textbf{a}) and Canneal (\textbf{b}).  “measured values” are the sensor data, and “minimum energy” is the minimum energy model prediction.
	}
	\label{fig:en_eq_freq_cores_fc}
\end{figure}
\subsection{Frequency $\times$ Input}
\cref{fig:en_eq_freq_inp_fi} plots the measured and modeled energy consumption for some of the applications modeled. The diagrams show some of the possible shapes that the model can take while varying the operating frequency, and input size.
\begin{figure}[H]
	\centering
	\captionsetup[subfigure]{justification=centering}
	\begin{subfigure}[b]{0.45\textwidth}
		\centerline{\includegraphics[width=\columnwidth]{models/figures/energy/freq_inps/completo_black_5.pdf}}
		\caption{}
		\label{fig:en_eq_black_fi}
	\end{subfigure}
	%
	\begin{subfigure}[b]{0.45\textwidth}
		\centerline{\includegraphics[width=\columnwidth]{models/figures/energy/freq_inps/completo_canneal_1.pdf}}
		\caption{}
		\label{fig:en_eq_canneal_fi}
	\end{subfigure}

	\caption{Example fit for a specific input size: Blackscholes (\textbf{a}) and Canneal (\textbf{b}).  “measured values” are the sensor data and “minimum energy” is the minimum energy model prediction.
	}
	\label{fig:en_eq_freq_inp_fi}
\end{figure}
\subsection{Cores $\times$ Input}
\cref{fig:en_eq_core_inp_ci} plots the measured and modeled energy consumption for some of the applications modeled. The diagrams  show some of the possible shapes that the model can take while varying the number of active cores, and input size.
\begin{figure}[H]
	\centering
	\captionsetup[subfigure]{justification=centering}
	\begin{subfigure}[b]{0.45\textwidth}
		\centerline{\includegraphics[width=\columnwidth]{models/figures/energy/cores_inps/completo_black_5.pdf}}
		\caption{}
		\label{fig:en_eq_black_ci}
	\end{subfigure}
	%
	\begin{subfigure}[b]{0.45\textwidth}
		\centerline{\includegraphics[width=\columnwidth]{models/figures/energy/cores_inps/completo_canneal_1.pdf}}
		\caption{}
		\label{fig:en_eq_canneal_ci}
	\end{subfigure}

@@

\subsection{Comparison}
The average results for each application were calculated using a model trained with only 10 configurations, and the comparison is displayed \cref{fig:mpe_svr_eq}. %We calculated the raw MPE values shown in ~\cref{tab:mpe_svr_eq}.
\begin{figure}[H]
	\centering
	\includegraphics[width=.8\columnwidth]{models/figures/mpe_svr_eq.pdf}
	\caption{Comparison of the mean percentage error between the proposed model and SVR. ``Model mean'' and ``SVR mean'' are the average of all MPE values for all applications.
	}
	\label{fig:mpe_svr_eq}
\end{figure}

@@

\section{Overheads on Training} \label{subsec:overhead}
It is known that machine learning is data-driven; in that sense, the SVR model obtained using only 10 configurations could be improved, but what about the analytical model? 
To answer that question, the proposed model and the SVR were also trained with a varying number of configurations.
We then compared the MPE and the amount of energy spent to create each model. 
This accuracy-energy trade-off is crucial since building models' energy overhead defeats the primary goal of saving power when running applications.
\enlargethispage{.5cm}

@@

\section{Analysis}
One of the most significant advantages of using an analytical model is the understanding of the problem that an equation provides, making many different kinds of analysis possible that are otherwise impossible with a machine learning model. In this section, we discuss one of the possible analyses. In the following figures, we try to understand the contribution of each parameter of the equation to the total energy consumption.

@@

\section{DVFS and DPM Optimization} \label{subsec:dvfs_optmin}
The effectiveness of the proposed approach during optimization was evaluated with a simple algorithm that finds the optimal frequency and number of active cores from the proposed equation. The results were then compared to the Linux default choices for power management.

>>>>

\subsection{Verifying Hypothesis} \label{subsec:ev_verifying_hypothesis}

@@

\subsection{Frequency and Voltage Relation} \label{subsec:ev_frequency_and_voltage Relation}
One of the assumptions was that the frequency and the voltage have a linear relationship, as indicated by ~\cref{eq:f_v}. To verify that, we build an experiment that sets the frequency to a specific value while sampling the voltage using the APERF and MPERF registers that provide feedback on the current CPU frequency. The average result of the sampling voltages is shown in  \cref{fig:freq_volt_rel}, where we can observe a near-perfect linear relation. This is because manufacturers implement this curve in the processors, using tables that relate ranges of frequencies to voltages so that they can precisely define any curve that will better suit their design.

@@

\subsection{Input Size and Instructions} \label{subsec:ev_input_size_and_instructions}
We ran the applications with different inputs assuming  linear growth in the amount of work for one input to the other when building our model. However, measuring and controlling the amount of work would require much instrumentation and tuning to find an input corresponding to a certain amount of work. Therefore, to build our models, we use the time to reference the amount of work, assuming that the work is proportional to the executing time. \cref{fig:time_input} corresponds to the verification of this supposition.

@@

\section{Fitting the Models} \label{subsec:fitting_the_models}
To find the parameters of  \cref{eq:en_final}, 10 uniformly random configurations of frequencies ($f$), cores ($p$) and inputs ($N$) were chosen from the range $1<=p<=32$, $1.2<=f<=2.2$ and $1<=N<=5$, respectively. The application was executed for each chosen configuration, and the measured energy and time values were collected. For the input size, if we assume that all CPU instructions take approximately the same time to execute, the number of basic operations will be directly correlated with the time. Thus, we can estimate the input size by looking at the execution time, allowing us to divide a large input size into several smaller ones, knowing their relationship, as performed in the work of Oliveira ~\cite{Oliveira2018ApplicationCharacterization}. The unity can also vary depending on the definition. For simplicity, we assign numbers from 1 to 10, increasing the problem linearly, so it is also possible to interpolate any input in between these values.

@@

\section{Measured versus Modeled Energy} \label{sec:measured_versus_modeled_energy}

@@

\subsection{Frequency $\times$ Cores} \label{subsec:mvme_frequency_x_cores}
\cref{fig:en_eq_freq_cores_fc} plots the measured and modeled energy consumption for some of the applications modeled. In addition,  some of the possible shapes that the model can take while varying the number of active cores, and operating frequency, are shown.%please confirm that the intended meaning has been retained.
% yes its the same

@@

	\caption{Example fit for a specific input size: Blackscholes (\textbf{a}) and Canneal (\textbf{b}).  “measured values” are the sensor data, and “minimum energy” is the minimum energy model prediction.
	}
	\label{fig:en_eq_freq_cores_fc}
\end{figure}

\subsection{Frequency $\times$ Input} \label{subsec:mvme_frequency_x_input}
\cref{fig:en_eq_freq_inp_fi} plots the measured and modeled energy consumption for some of the applications modeled. The diagrams show some of the possible shapes that the model can take while varying the operating frequency, and input size.
\begin{figure}[H]
	\centering
	\captionsetup[subfigure]{justification=centering}
	\begin{subfigure}[b]{0.45\textwidth}
		\centerline{\includegraphics[width=\columnwidth]{models/figures/energy/freq_inps/completo_black_5.pdf}}
		\caption{}
		\label{fig:en_eq_black_fi}
	\end{subfigure}
	%
	\begin{subfigure}[b]{0.45\textwidth}
		\centerline{\includegraphics[width=\columnwidth]{models/figures/energy/freq_inps/completo_canneal_1.pdf}}
		\caption{}
		\label{fig:en_eq_canneal_fi}
	\end{subfigure}

	\caption{Example fit for a specific input size: Blackscholes (\textbf{a}) and Canneal (\textbf{b}).  “measured values” are the sensor data and “minimum energy” is the minimum energy model prediction.
	}
	\label{fig:en_eq_freq_inp_fi}
\end{figure}

\subsection{Cores $\times$ Input} \label{subsec:mvme_cores_x_input}
\cref{fig:en_eq_core_inp_ci} plots the measured and modeled energy consumption for some of the applications modeled. The diagrams  show some of the possible shapes that the model can take while varying the number of active cores, and input size.
\begin{figure}[H]
	\centering
	\captionsetup[subfigure]{justification=centering}
	\begin{subfigure}[b]{0.45\textwidth}
		\centerline{\includegraphics[width=\columnwidth]{models/figures/energy/cores_inps/completo_black_5.pdf}}
		\caption{}
		\label{fig:en_eq_black_ci}
	\end{subfigure}
	%
	\begin{subfigure}[b]{0.45\textwidth}
		\centerline{\includegraphics[width=\columnwidth]{models/figures/energy/cores_inps/completo_canneal_1.pdf}}
		\caption{}
		\label{fig:en_eq_canneal_ci}
	\end{subfigure}

@@

\section{Comparison} \label{sec:comparison}
The average results for each application were calculated using a model trained with only 10 configurations, and the comparison is displayed \cref{fig:mpe_svr_eq}. %We calculated the raw MPE values shown in ~\cref{tab:mpe_svr_eq}.
\begin{figure}[H]
	\centering
	\includegraphics[width=.8\columnwidth]{models/figures/mpe_svr_eq.pdf}
	\caption{Comparison of the mean percentage error between the proposed model and SVR. ``Model mean'' and ``SVR mean'' are the average of all MPE values for all applications.
	}
	\label{fig:mpe_svr_eq}
\end{figure}

@@

\section{Overheads on Training} \label{subsec:overhead_on_training}
It is known that machine learning is data-driven; in that sense, the SVR model obtained using only 10 configurations could be improved, but what about the analytical model? 
To answer that question, the proposed model and the SVR were also trained with a varying number of configurations.
We then compared the MPE and the amount of energy spent to create each model. 
This accuracy-energy trade-off is crucial since building models' energy overhead defeats the primary goal of saving power when running applications.
\enlargethispage{.5cm}

@@

\section{Analysis} \label{sec:analysis}
One of the most significant advantages of using an analytical model is the understanding of the problem that an equation provides, making many different kinds of analysis possible that are otherwise impossible with a machine learning model. In this section, we discuss one of the possible analyses. In the following figures, we try to understand the contribution of each parameter of the equation to the total energy consumption.

@@

\section{DVFS and DPM Optimization} \label{sec:dvfs_dpm_optminzation}
The effectiveness of the proposed approach during optimization was evaluated with a simple algorithm that finds the optimal frequency and number of active cores from the proposed equation. The results were then compared to the Linux default choices for power management.

### 2022-04-27 thesis/pascalanalyzer/pascalanalyzer.tex
carlos revision 1
change subsection to section and labels

\subsection{Introduction} \label{sec:introduction_pascal}

@@

\subsection{Related Works} \label{sec:related_work_pascal}

@@

\subsection{Design and Features} \label{sec:design_and_features_pascal}

This section presents the architecture, components, and interconnections used in the design of the proposed tool. It also includes a discussion about main features, instrumentation modes, and output file structure that contains the data measured and collected by the proposed tool.

\subsubsection{Architecture} \label{subsec:architecture_pascal}
The tool we propose to measure, combine and compare multiple runs of a parallel application implements two main concepts to achieve this goal: actuators and sensors.

@@

\subsubsection{Instrumentation and Intrusiveness} \label{subsec:intrusiveness_pascal}

@@

\begin{figure}[H]
\centering
\captionsetup{justification=centering}
\begin{subfigure}[b]{0.45\textwidth}	
	\includegraphics[width=\textwidth]{pascalanalyzer/figures/designfeatures/instrumentation_overhead_summary.pdf}
	\caption{\centering}
	\label{fig:overhead_1}
\end{subfigure}
%
\begin{subfigure}[b]{0.46\textwidth}
	\includegraphics[width=\textwidth]{pascalanalyzer/figures/designfeatures/instrumentation_overhead_boxplot.pdf}
	\caption{\centering}
	\label{fig:overhead_2}
\end{subfigure}
\caption{Measuring variance of the time to single instrumentation, 
	%MDPI: 1. For this figure, please use the scientific notations.
	%          2. Please add commas to numbers in the Ox axis of the figures, e.g.: 20,000 30,000 40,000 etc. - CHANGED
	i.e., a call to {\tt analyzer\_start} and {\tt analyzer\_stop} while varying the number of measurements. (\textbf{a}) Time consumed from sampling a region one time in seconds. %MDPI: We moved the explanations of subfigures here, please confirm.
	(\textbf{b}) Box plot showing the statistics of the sampling time of a single region.}
\label{fig:overhead}
\end{figure}

@@

\subsubsection{Features and Usage} \label{subsec:features_and_usage_pascal}

@@

\subsubsection{Exported Data Structure} \label{subsec:datastructure_pascal}

>>>>

\section{Introduction to profiling tools} \label{sec:introduction_to_profiling_tools}

@@

\section{State of the art: profiling and tracing tools} \label{sec:state_of_the_art_profiling_and_tracing_tools}

@@

%\section{Design and Features} \label{sec:design_and_features}
%
%This section presents the architecture, components, and interconnections used in the design of the proposed tool. It also includes a discussion about main features, instrumentation modes, and output file structure that contains the data measured and collected by the proposed tool.

\section{Pascal architecture} \label{sec:pascal_architecture}
The tool we propose to measure, combine and compare multiple runs of a parallel application implements two main concepts to achieve this goal: actuators and sensors.

@@

\section{Instrumentation and Intrusiveness} \label{sec:instrumentation_and_intrusiveness}

@@

\begin{figure}[H]
\centering
\captionsetup{justification=centering}
\begin{subfigure}[b]{0.45\textwidth}	
	\includegraphics[width=\textwidth]{pascalanalyzer/figures/designfeatures/instrumentation_overhead_summary.pdf}
%	\caption{\centering}
	\label{fig:overhead_1}
\end{subfigure}
%
\begin{subfigure}[b]{0.46\textwidth}
	\includegraphics[width=\textwidth]{pascalanalyzer/figures/designfeatures/instrumentation_overhead_boxplot.pdf}
%	\caption{\centering}
	\label{fig:overhead_2}
\end{subfigure}
\caption{Measuring variance of the time to single instrumentation, 
	%MDPI: 1. For this figure, please use the scientific notations.
	%          2. Please add commas to numbers in the Ox axis of the figures, e.g.: 20,000 30,000 40,000 etc. - CHANGED
	i.e., a call to {\tt analyzer\_start} and {\tt analyzer\_stop} while varying the number of measurements. (\textbf{a}) Time consumed from sampling a region one time in seconds. %MDPI: We moved the explanations of subfigures here, please confirm.
	(\textbf{b}) Box plot showing the statistics of the sampling time of a single region.}
\label{fig:overhead}
\end{figure}

@@

\section{Features and Usage} \label{sec:features_and_usage}

@@

\section{Exported Data Structure} \label{sec:exported_data_structure}

### 2022-04-27 thesis/phases/phases.tex
change subsection to section and labels

\section{Model with phases}

@@

\section{Introduction}
Talk about the importance of energy efficiency.

\section{Related work}
Some related work

\section{Methodology}

\section{Optimal energy configuration}
Splitting a program into phases, or time intervals with a selected set of execution parameters, has an impact on energy consumption. To find the ideal phase division, we need to compute the optimal energy configuration for a given number and duration of phases. For that, many different approaches could be applied, each having different trade-offs.

@@

\section{Data Collection}
Data, power samples, can be gathered by running the application in several possible context configurations. In a system with 32 cores that can run at 13 frequencies, we can have 416 (32*13) possible configurations. Power samples can be taken from dedicated sensors in the IPMI system [REF]. To avoid overload, a sample rate of 0.5 seconds is more than sufficient. Additionally, the behavior of an application can be affected by the workload, so it is also interesting to run applications with different inputs and assess their impact on the collected data [REF victor alex paper].

@@

\section{The simulator}
To analyse the impact of configurations and identify optimal time-intervals, phases, we propose an integrator, which computes the energy on an interval for a given configuration, and a reference, a brute force test of all possible combinations. The integrator has order zero, and computers the energy between two timestamps, as shown in the figure \ref{fig:zero_order}, where the red and yellow parts area are the energy value.

@@

\section{Optimizing phases}
The main goal of this section is to identify the optimal number and duration of time intervals. Indeed, several short phases can have an impact on switching overhead as well as few long phases on the overall energy.

@@

\section{Results}

@@

\section{Conclusion and future work}
The main conclusion of this work was that in HPC enviroment we don't need a lot of phases to optimize the energy consumption given that for one phase we can compute the optimal energy.

The final idea is to use the information of the best phase to find a performance metric that can provide us this division, in future work we intend to compute this metrics using combination of hardware performance counters enabling optimal phase division in real time. This can improve current DVFS algorithms giving them an workload metric that can improve the energy savings.

>>>>

\section{Model with phases} \label{sec:model_with_phases}

@@

\section{Introduction to models on time} \label{sec:introduction_to_models_on_time}
Talk about the importance of energy efficiency.

\section{Related work: Phases} \label{sec:related_work_phases}
Some related work

\section{Optimal energy configuration} \label{sec:Optimal_energy_configuration}
Splitting a program into phases, or time intervals with a selected set of execution parameters, has an impact on energy consumption. To find the ideal phase division, we need to compute the optimal energy configuration for a given number and duration of phases. For that, many different approaches could be applied, each having different trade-offs.

@@

\section{Data Collection} \label{sec:data_collection}
Data, power samples, can be gathered by running the application in several possible context configurations. In a system with 32 cores that can run at 13 frequencies, we can have 416 (32*13) possible configurations. Power samples can be taken from dedicated sensors in the IPMI system [REF]. To avoid overload, a sample rate of 0.5 seconds is more than sufficient. Additionally, the behavior of an application can be affected by the workload, so it is also interesting to run applications with different inputs and assess their impact on the collected data [REF victor alex paper].

@@

\section{The simulator} \label{sec:the_simulator}
To analyse the impact of configurations and identify optimal time-intervals, phases, we propose an integrator, which computes the energy on an interval for a given configuration, and a reference, a brute force test of all possible combinations. The integrator has order zero, and computers the energy between two timestamps, as shown in the figure \ref{fig:zero_order}, where the red and yellow parts area are the energy value.

@@

\section{Optimizing phases} \label{sec:optimizing_phases}
The main goal of this section is to identify the optimal number and duration of time intervals. Indeed, several short phases can have an impact on switching overhead as well as few long phases on the overall energy.

@@

\section{Results: Phases experiments} \label{sec:results_phases_experiments}

@@
